Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-16 paper-2023-acsos-pulverization.tex
Introductory concepts on deployment and reconfiguration -- possono essere utili @danysk ?

>>>>

\subsection{Deployment and Reconfiguration: Basic Concepts}

The \emph{deployment view} is a well-known architectural viewpoint for software systems,
concerned with the mapping of \emph{software components} to \emph{physical machines}~\cite{DBLP:journals/software/Kruchten95}
 and supported by modelling notations like \emph{UML Deployment diagrams}.
%
Here, we provide a brief introduction to deployment and reconfiguration, based on the conceptual characterisation of~\cite{DBLP:journals/jss/ArcangeliBL15,carzaniga1998characterization}.
%
A \emph{site} is a set of computers (\emph{hosts}) that may host a \emph{software system}, i.e., a coherent collection of artifacts.
%
\emph{(Software) Deployment} is the process of moving and making a software product available and operational from one or more \emph{producer sites} to a target \emph{deployment domain} (i.e., a set of \emph{consumer sites}).
%
The \emph{deployment plan} defines 
 the mapping between the software system
 and the deployment domain,
 augmented with further information (e.g., metadata).
%
Deployment-related activities 
 include: (i) \emph{release/update} of the software system at the producer site;
 (ii) \emph{installation/deinstallation} at/from the consumer sites;
 (iii) \emph{activation/deactivation}, for starting/stopping the components;
 (iv) \emph{reorganisation} of the software system;
 and (v) \emph{redistribution}, i.e., changing the deployment plan.
